Algorithm explanation

### 2013-08-28 article/future.tex
Future work

\paragraph{Solving linear constraints}

Although we solve the constraints by a general SMT solver Z3, GNU
Linear Programming Kit (GLPK) may be sufficient for solving
constraints.  The linear programming solver should support sparse
matrix because our algorithm generates constraints that are sparse.

\paragraph{Generation and choice of unsatisfiable core}
Our Horn clause solver make use of Z3 to obtain an unsatisfiable core
from the linear constraints.  However the extraction of unsatisfiable
core from the proof may cost certain level of computation.
Originally, it is better that the theorem prover customizes to extract

>>>>

\paragraph{Solving linear constraints}
Although we solve the constraints by a general SMT solver Z3, GNU
Linear Programming Kit (GLPK) may be sufficient for solving
constraints.  The linear programming solver should support sparse
matrix because our algorithm generates constraints that are sparse.

\paragraph{Generation and choice of unsatisfiable core}
We can efficiently build linear constraints for the given $G$ after
the transformation in $\transGraph$~procedure by appropriate inference
from the previous constraint and the SMT query result.  Our Horn
clause solver make use of Z3 to obtain an unsatisfiable core from the
linear constraints.  However the extraction of an unsatisfiable core
from the proof sums up to a large portion of the whole computation
time in our algorithm.

Although our implementation in this work did not consider such the way
of optimization to reduce the cost of linear constraints queries, it
is necessary to reduce the number of them for reduce the computation
cost.  For instance, the optimization is possible by appropriatealy
updating $V_\star$ in $\solveHorn$~procedure since the vertices that
are already examined for split does not need to be considered again.

The choice of subset of constraints for an unsatisfiable core is also
important.  In some cases, there exists different multiple cores and
the algorithm returns a different shape of the solution in relation to
the choice of them.  Thus, we need further study to optimize the order
of choice of multiple unsatisfiable cores if ones exists.

\paragraph{Separation of edges}
To transform the graph by $\transGraph$~procedure, there may be
multiple transformations possible.  For example, consider a predicate
variable $P$ and edges $\left\lbrace e_1, e_2, e_3, e_4 \right\rbrace$
that go out from the vertex.  If an unsatisfiable core contains a set
of edges $\left\lbrace e_1, e_2 \right\rbrace$,
$\transGraph$~procedure determines to split those edges by duplicating
$P$.  However at this point, $e_3$ and $e_4$ are free to be connected
to any duplication of $P$.  Alghough our current algorithm split
$\left\lbrace e_1, e_2, e_3, e_4 \right\rbrace$ into four duplications
$\left\lbrace e_1 \right\rbrace$ to $\left\lbrace e_4 \right\rbrace$,
it is possible to split into $\left\lbrace e_1, e_3\right\rbrace$ and
$\left\lbrace e_2, e_4 \right\rbrace$ for example.  By intellilgently
choose this, we may be able to obtain much simpler solution than the
current algorithm.

We suggest to reduce this edge split problem into a graph coloring
problem.  By generating a graph which a set of vertices have an edge
of Horn graph as a label and solve a coloring problem on it, the
algorithm can wisely determine the minuminm number of duplications.

\paragraph{Support for Horn clauses with Recursions}
Considering usages of Horn clause solving in program verification, it
is useful to update our algorithm so that it can solve Horn clauses
with recursions as well. For instance, this makes possible to generate
invariants upon the loop programs on the control flow graphs, rather
than to generate a set of disjunctive constraints
\cite{conf/pldi/BeyerHMR07}.

One known method to let the algorithm support Horn clauses with
recursions is to unroll a looping predicate in the problem
\cite{conf/ppdp/UnnoK09}.  By computing a fixedpoint of the predicate
solution over unrolled programs, it is possible to virtually solve
Horn clauses with recursions as well.
